Deep Reinforcement Learning for Conservation Decisions

### 2021-05-26 manuscript/manuscript.Rmd
Marginal slow improvement here. Still trying to frame the reward paragraph

<!-- reason 1: instability-->
<!-- ML: pivoting this to generalizability but still rewrote past paragraph which might fit in the appendix somewhere-->
Currently, deep RL agents struggle to generalize their skills [@generalization].
This inability can be observed in training: if you train an agent on an environment that demands learning a wide range of tasks, the agent will likely fail to converge to an optimal policy [@CITE].
And, during evaluation, if you give an agent any novel task, including tasks that are closely related to the examples that the agent saw in training, the agent will likely fail to generalize its policy to this new situation [@CITE].
These failures are all due to the brittleness of deep neural networks. 
Across deep learning, neural networks tend to perform exceptionally well on narrowly specified problems, yet neural networks show great fragility when given new situations or problem statements that require flexibility [@CITE].

@@

<!--
Under some conditions, RL agents can prove adept at _transfer learning_, in which an agent trained in one environment performs well under a different environment.
-->
<!-- if we're really recommending 'testing' for stability, maybe we need to demo that in the appendix-->

<!-- reason 2: interpretability -->
<!-- ML: Re our OU talk, might be worth saying that this is a barrier to adoption? If we want to ultimately use these RL agents to make important decisions, it would be hard to swallow us blindly using them without having any sense to what is going on. -->
Interpretability is an issue that may hinder the adoption of deep RL methods [@cite].

Although there have been some attempts to increase the transparency of RL agents that use neural network as function approximators [cite], it is still very difficult to explain the behavior of RL-trained agents.
As our examples have illustrated, it may be possible to gain intuition on an agent's behavior by visualizing the action selected against each possible state, though this becomes more difficult in large problems.
Another challenge is that Deep RL algorithms are very sample inefficient, all though progress is being made to improve this [@cite]. <!-- ML: I think we can cut this sentence, mentionned it in passing earlier-->
-->

<!-- reason 3: reward design -->
<!-- ML: I'll take a pass at this paragraph in a new branch. I think it would be useful to put terms on stuff in here, like reward shaping and reward hacking which we are talking around. -->
An issue that is central to any applied optimization problem is using the right objective.
There have been many examples in which explicit reward design goes very wrong [cite].
And for ecological systems, which are often very complex and impossible to fully observe, it seems that bad reward design is quite likely.
Moreover, specifying a reward function for conservation brings up various ethical concerns -- e.g. who gets to specify the reward function and will the values of the greater community be represented in the reward function.
RL researchers often introduce modified reward functions during training that help an agent perform better on the original objective [@cite].
This approach is particularly common when rewards are sparse, such as in a game of Chess where the only objective that counts is whether or not you win, but during training, an RL algorithm may reward the agent for intermediate steps such as capturing a piece.

>>>>

<!-- reason 1: generalizability-->
<!-- ML: pivoting this to generalizability but still rewrote past paragraph which might fit in the appendix somewhere-->
Currently, deep RL agents struggle to generalize their skills [@generalization].
This inability can affect performance during training and at evaluation. 
For instance, training an agent on an environment that demands learning an assortment of skills is typically much more difficult than training an agent to learn one specific skill [@CITE].
And, at evaluation, if you give an agent a novel task, including tasks that are closely related to the examples that the agent saw in training, the agent will likely fail to generalize its learned behavior to this new situation [@CITE].
These failures are all due to the brittleness of deep neural networks. 
Across deep learning, neural networks tend to perform exceptionally well on narrowly specified problems, yet neural networks show great fragility when given new situations or problem statements that require flexibility [@CITE].
The ability to adapt to new situations is critical for any decision-making problem in the real world, so the current lack of this ability in deep RL may limit deep RL's effectiveness to conservation issues.

@@

<!--
Under some conditions, RL agents can prove adept at _transfer learning_, in which an agent trained in one environment performs well under a different environment.
-->
<!-- if we're really recommending 'testing' for stability, maybe we need to demo that in the appendix-->
<!-- reason 2: interpretability -->
<!-- ML: Re our OU talk, might be worth saying that this is a barrier to adoption? If we want to ultimately use these RL agents to make important decisions, it would be hard to swallow us blindly using them without having any sense to what is going on. -->
Compounded with their difficulties to generalize, deep RL agents also suffer from an inability to be fully interpreted [@cite].
Deep neural networks are commonly referred to as black box models, since it is not currently possible to explain why a deep neural network produces a specific output from a given input.
In the context of deep RL, this means that we cannot explain why an agents makes a decision besides that the agent is attempting to maximize cumulative rewards.
The lack of explainability dovetails dangerously with generalizability concerns. 
Because we are not able to interpret deep RL agents, we are not able to anticipate how an agent will behave when in an unfamiliar situation.
Despite limited progress to make neural networks more explainable, interpretability will likely be a concern that limits adoption.

<!-- reason 3: reward design -->
<!-- ML: I'll take a pass at this paragraph in a new branch. I think it would be useful to put terms on stuff in here, like reward shaping and reward hacking which we are talking around. -->
A fundamental issue for all applied optimization problems is using the right objective.
There have been many examples in which explicit reward design produces unanticipated agent behavior that is highly undesirable [@CITE].
For ecological systems, which are typically very complex and difficult to fully understand, it seems that bad reward design is quite likely.
To avoid these undesirable outcomes, RL researchers often *shape* the reward functions so that the agent can more easily learn a good-performing policy [@cite].
This approach is particularly common when rewards are *sparse*, such as in a game of Chess where the objective is to win and there are no true immediate rewards.
In this case, one might shape the reward function so that the agent is awarded for capturing the opponent's pieces, but this could easily lead to a policy where the agent focuses on capturing pieces instead of winning the game.
Since benefits in conservation typically come long after their corresponding actions, sparse reward.
Moreover, specifying a reward function for conservation brings up various ethical concerns -- e.g. who gets to specify the reward function and will the values of the greater community be represented in the reward function.
